Online {\IterComp}

### 2017-11-16 infra.tex
infra minor

    Although {\itercomp} had been originally proposed as an \textit{offline} optimization strategy, this work shows that this powerful
    technique can be adapted to work in \textit{online} scenarios. Figure~\ref{fig:infra-diagram} shows an overview of how our online
    {\itercomp} mechanism works. On the developers' side, we would traditionally produce an application binary optimized for the inputs
    provided by them. In our approach instead, the program is pre-compiled to LLVM Intermediate Representation (IR) without optimizations,
    is instrumented to measure the amount of work performed and the wall-clock time, and is bundled with the {\itercomp} mechanism.
    On the user's side, this mechanism selects an optimization sequence and compiles the instrumented IR to binary using this sequence.
    Next time the user runs the application, we load and execute the latest binary and measure its work and execution time. We accumulate
    multiple such measurements, executing each input only once, until we can estimate the work efficiency of this optimization sequence
    with high confidence. Finally, we use this information to help us select the next optimization sequence.

@@

    Another component, the \textit{Search Driver}, is responsible for guiding the optimization process. Each selected optimization sequence
    is used for multiple executions of the program in order to gather enough work efficiency measurements. When we are able to
    estimate this work efficiency with a confidence interval narrower than a certain threshold, we can start evaluating a different
    optimization sequence. We call the number of executions performed using the same optimization sequence the \textit{Input-Window Size}.
    \FIXME{MORE. How does the new search work?}

@@

    Most devices have distinct idle and peak usage periods. For example, mobile devices are used intensely during the day and not at all while
    the user is sleeping and the battery is charging~\citep{mpeis16}. Many researchers have identified similar idle and peak usage periods in
    the context of data centers~\citep{armbrust10,chen12b}. The proposed \itercomp infrastructure is very well suited to such scenarios. In
    particular, we can use periods of idleness or underutilization to select the next few optimization sequences to try and compile the
    corresponding binaries. This approach effectively hides the compilation overhead from the user. During peak periods, we only have to select
    which of the existing binaries to evaluate which introduces almost no overhead.

>>>>

    Although {\itercomp} had been originally proposed as an \textit{offline} optimization strategy, this work shows that this powerful
    technique can be adapted to work in \textit{online} scenarios. Figure~\ref{fig:infra-diagram} shows an overview of how our online
    {\itercomp} mechanism works. On the developers' side, we would traditionally produce an application binary optimized for the inputs
    provided by them. In our approach instead, the program is pre-compiled to LLVM Intermediate Representation (IR) without optimizations
    and is instrumented to measure the amount of work performed and the wall-clock time.
    On the user's side, the online iterative compilation mechanism selects an optimization sequence and compiles the instrumented IR to binary using this sequence.
    Next time the user runs the application, we load and execute the latest binary and measure its work and execution time. We accumulate
    multiple such measurements, executing each input only once, until we can estimate the work efficiency of this optimization sequence
    with high confidence. Finally, we use this information to help us select the next optimization sequence.

@@

    Another component, the \textit{Search Driver}, is responsible for guiding the optimization process. Each selected optimization sequence
    is used for multiple executions of the program in order to gather enough work efficiency measurements. When we are able to
    estimate this work efficiency with a confidence interval narrower than a certain threshold, we can start evaluating a different
    optimization sequence.

@@

    Most devices have distinct idle and peak usage periods. For example, mobile devices are used intensely during the day and not at all while
    the user is sleeping and the battery is charging~\citep{mpeis16}. Many researchers have identified similar idle and peak usage periods in
    the context of data centers~\citep{armbrust10,chen12b}. The proposed \itercomp infrastructure is very well suited to such scenarios. In
    particular, we can use periods of idleness or underutilization to select the next few optimization sequences to try and to compile the
    corresponding binaries. This approach effectively hides the compilation overhead from the user. During peak periods, we only have to select
    which of the existing binaries to evaluate which introduces almost no overhead.
